*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-04 Code/Manuscript_O2.Rmd
Added Data availability section- moved text there

*In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the duration of the lag phase, if any. All data obtained from the Multicultivator were saved as comma separated values files  (https://github.com/FundyPhytoPhys/prochlorococcus_o2/).

@@

Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll specific growth estimates fitted from the high resolution ΔOD measurements for each tube in a Multicultivator. The residuals of the logistic growth curve fit are shown and the growth spectral waveband is plotted and illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
(h). Annotated code for data import, transformations and analyses is available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/  MAKE SURE RePOSTIORY IS PUBLICXXXX

@@

# Acknowledgements  {.unnumbered}
Jonah Sheinin (Mount Allison Student) assisted with growth of some cultures for protein analyses, while Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.

# Funding  {.unnumbered}
To Be Entered through PLoSONe system and deleted here
Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)

>>>>

*In situ* measurements of Optical Density (OD) 680 nm, a proxy for cell suspension density, cell size dependent scatter and cell chlorophyll content;  and OD 720 nm, a proxy for cell suspension density and cell size dependent scatter, were recorded every 5 minutes over least 8 to 14 days,  depending on the duration of the lag phase, if any.

@@

Figure \@ref(fig:deltaODLogGrowthPlot) is an example of chlorophyll specific growth estimates fitted from the high resolution ΔOD measurements for each tube in a Multicultivator. The residuals of the logistic growth curve fit are shown and the growth spectral waveband is plotted and illustrates the imposed PAR (µmol photons m^-2^ s^-1^) and photoperiod
(h).

@@

# Data availability  {.unnumbered}
All data obtained from the Multicultivator were saved as comma separated values files and are available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/Data/RawData.
Annotated code for data import, transformations and analyses are available at https://github.com/FundyPhytoPhys/prochlorococcus_o2/Code.

# Acknowledgements  {.unnumbered}
Carlie Barnhill (Mount Allison Student) assisted with code for import of multicultivator growth data files.

XXX PLOS requires grant numbers XXX
# Funding  {.unnumbered}
To Be Entered through PLoSONe system and deleted here
Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)
